
**dismolib** is an interactive library for simulating the numerical outcomes of published mathematical epidemiology models including two types of COVID-19 models!
  
  For a disease model in this library, you can:
  
  <ul>
  <li>Vary the parameters</li>
  <li>Simulate the time course</li>
  <li>Perform stability analysis</li>
  <li>And so much more.. </li>
  </ul> 
  
### <span style="color:navy">Get Started!</span>
 
* Select a disease in the 
```{r, eval = T, echo=FALSE, results='asis'}
 text = actionLink("modelTab","Models")
print(text)
``` 
tab
* Understand the flowchart
* Explore the health states/compartments by clicking on Species
* Explore the parameters by clicking on Global Quantities
* Run a Task like Time Course or Stability Analysis
* Download the model as a COPASI (.cps) or an SBML (.xml) file to make changes
* Read more about each model and its analysis in 
```{r, eval = T, echo=FALSE, results='asis'}
 text = actionLink("doc","Documentation")
print(text)
``` 
tab
* [Download](http://copasi.org/Download/) COPASI to create your own models
